---
title: "What are the different theories on the origin of life?"
description: |
  In this article we will talk about the differents theories on the origin of life.
author:
  - name: Florent Malherbe
    url: {}
date: 11-01-2019
preview: earth image 
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}
![](earth image)
```


#####Words : 813

##Vocabulary

##Analysis table


| Researchers         | Miller and Urey, Alexander Graham                                                                                                                                                                                                      |
| ------------------- | --------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| PUBLISHED IN        | Livescience.com                                                                                                                                                                                                                         |
| GENERAL TOPIC       | 7 theories of origin of life                                                                                                                                                                                                 |
| PROCEDURE           | In the article  |
| CONCLUSIONS         | Life can't appear with simple molecules and can't be create just in the air                                                                                                                                                                   |
| REMAINING QUESTIONS | How the life was created on our planet if it's not spontaneous                                                                                                                                                                                |


Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

<https://www.livescience.com/13363-7-theories-origin-life.html>

